Solutions to Integer Programming from Quantum Annealing

### 2020-05-08 paper/main.tex
push for catalina update

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}. This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer. Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions. In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
\begin{align}
&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2.
\end{align}

>>>>

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}. This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer. Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions. In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
\begin{align}
&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
\end{align}
and gives the probability of randomly guessing the MDS of $G(n)$.
